---
title: "Vermillion HW2"
author: "Monica Vermillion"
date: "February 4, 2019"
output:
  pdf_document: default
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Questions 1 
(a) 
```{r,echo=false}
setwd("H:/HierarchicalModel/Homework/homework2-master") 
seeds<- read.csv("Seeds.csv")
catfish<- read.csv("catfish_survival.csv")
mosquito<- read.csv("mosquito_data.csv")
seedSurv<- read.csv("SEEDLING_SURVIVAL.csv")


# Question 1: Using Seedling Survival 
plot(survival~HEIGHT,data=seedSurv,main='Seed Survival and Height',col="darkseagreen4",pch=19,
     xlab="Seed Survival",ylab = "Seed Height")
M1<-glm(survival~HEIGHT,data=seedSurv,family="binomial")
coef(M1)
curve(plogis(-0.06271111*x+0.140711),add=T)


```

(b)
```{r, eco= false}
# Question 1: Using Seedling Survival
#(b)
plot(seedSurv$survival~seedSurv$LIGHT,main='Seed Survival and Light',col="darkseagreen4",pch=19,
     xlab="Seed Survival",ylab = "Amount of Light")
M2<-glm(survival~LIGHT,data = seedSurv, family="binomial")
coef(M2)
curve(plogis(2.66194*x-0.06552),add=T)


```
Is height or light a stronger predictor of seedling survival?
The amount of light a seed gets is a much stronger predictor of seedling survival compared to the seed height. 





Queston 2: Dataset: Seeds.csv
Predictor variable chosen: Light 

```{r}
#Binomial Regression
proport<-(seeds$recruits/seeds$seeds) # make the data proportional; total sucesses/ total trials
response<-cbind(seeds$recruits, seeds$seeds-seeds$recruits)

plot(proport~seeds$light,main='Seed and Light Response',col="darkseagreen4",pch=19,
     xlab="Amount of Light",ylab = "Seed Survival")
M3<-glm(response~seeds$light,family="binomial")
coef(M3)
curve(plogis(-3.093+0.0798*x),add=T)



```








Question 3: mosquito data
(a)&(b)  


```{r}
normEgg<- (mosquito$Emergent_adults/mosquito$Egg_Count)
mosResponse<- cbind(mosquito$Emergent_adults, mosquito$Egg_Count-mosquito$Emergent_adults)
plot(normEgg~mosquito$Detritus,main='Mosquito and Detritus Response',col="darkseagreen4",pch=19,
     xlab="Amount of Detritus",ylab = "Mosquitos")

M4<-glm(mosResponse~mosquito$Detritus,family="binomial")
coef(M4)
curve(plogis(1.321-0.3216083*x),add=T)
curve(plogis(1.44-0.19*x-0.21*x^2+0.04*x^3), add=T,col="darkcyan")
curve(plogis(-10*x*exp(1)^(-2*x)), add=T,col="brown4")

```

(c) How are the biological implicatons of the polynomial model different from the Ricker model? 
The ricker model implies that the initally there is a lower impact of detritus initally on the number of moquitoes which starts to increase and then taper out. Where the polynomial model shows a constant negative relationship between the amount of detritius and the number of adult moquitos. 

(d) 
```{r}
# Using the polynomial model 
-sum(dbinom(x=mosquito$Emergent_adults,size=mosquito$Egg_Count,              
prob=plogis(1.44-0.19*mosquito$Detritus-0.21*mosquito$Detritus^2+0.04*mosquito$Detritus^3),log=T))
# Using the Ricker model 
-sum(dbinom(x=mosquito$Emergent_adults,size=mosquito$Egg_Count,              
prob=plogis(-10*mosquito$Detritus*exp(1)^(-2*mosquito$Detritus)),log=T))

```


(e) According to dbinom, the likelihood of the data is higher for the ricker model at a likelyhood of 2739.501 compared to a likelihood of 2739.501 for the polynomial model. 

Question 4: Power Analysis 

```{r}
#1 predefine true slope, intercept and sd
slope=-4
inte = 7.56
std=1.2
#2 Create a predictor variable 
pre<- seq(from=.36, to=0.87, length.out=98) # predictor variable 
#3 Create a vector of sample size 
sample_size<-c(3:100) #sample size 
# Preallocate your vector to fill 
power_vector<-rep(NA,times=97) # preallocate variable 
P_value <- rep(NA,times=97) #preallocate variable 

# 5 write for loop 
for(i in 1:length(sample_size)) {
  sim<-rnorm(n=sample_size[i],mean=inte+slope*pre[i],sd=0.8)
  Model<-glm(sim~pre[1:(i+2)])
  power_vector[i]<-coef(Model)[2]
  P_value[i] <- summary(Model)$coefficients[4]
 }

plot(power_vector~sample_size)
abline(h=-4)

MSE=function(y,y_hat)
{ 
  return ((y-y_hat)^2)
}
true_slope <- rep(slope,length(sample_size))
Ln_MAE <- MSE(power_vector,true_slope)

plot(P_value~sample_size)

```

Binomal 


```{r} 
# Preallocate your vector to fill 
power_Binom<-rep(NA,times=97) # preallocate variable 
P_binom <-rep(NA,times=97) 
# 5 write for loop 
for(i in 1:length(sample_size)) {
  fertalizer_amount <- seq(from=20, to=50, length.out=sample_size[i]) 
  b_sim<-rbinom(n=sample_size[i],size=50,prob=plogis(inte+slope*fertalizer_amount))
  Model_binom<-glm(b_sim~fertalizer_amount)
  power_Binom[i]<-coef(Model_binom)[2]
  P_binom[i] <- summary(Model_binom)$coefficients[2,4]
 }

plot(power_Binom~sample_size)
abline(h=-4)

Binom_MAE <- MSE(power_Binom,true_slope)

```

(a) For my linear regression I would need more than 20 samples. I could not get my bionomial regression to work correctly. 

B. to ensure a p_value less than 0.05 I would have to run the samples for a much larger size. None of my Pvalues were around 0.5 

C. In general, statical power is generally higher for continuous data compared to discrete because continous data should follow a gradient if it fits a model where discrete data is not going to fit any model well because it either is or isn't. 
























